Paper TITLE

### 2016-08-03 code/Papeeeer.Rmd
pap

---
title: "Paper TITLE"
output: html_document
---

@@

@@

@@

@@

@@

>>>>

---
title: "Paper TITLE"
output: pdf_document
---

@@

Cleaning data
Initially, the dataset is split into fifteen datasets, one for each odd year between 1985 and 2013. Due to differences in how the survey was conducted over the years, each dataset has varying column names and positions, and, for surveys performed earlier than 2003, missing columns. To standardize the data, we used the format of the more modern datasets, i.e the datasets from 2003 to 2013. Thus, we begin by appending a column onto each dataset to mark which year that data was gathered, remove an extraneous column from the 2009 dataset, and then simply combine the datasets. For the older years, the datasets must again be split into two groups as some columns are named differently and do not fit with our standard. Once we rename the columns, we add the missing columns that dictate the raw, adjusted by growth, and adjusted by people income limits for each household. These income limits specifically determine what the extremely low income bracket is for the area each household is in. For each list of datasets, we reorder the columns to exactly match that of our base, the datasets gathered from 2003 onward. Finally we combine every list of datasets into a single dataset, and then store it in a comma separated file called combined_years.

@@

As pictured in the graph, the relationship between household income and burden is seen as a positive correlation. From the graph, you can see that higher income household have less burden to deal with, which makes sense because those with more money are able to pay off monthly costs more easily. Those with 50% more burden are near the poverty line. From this graph, you can see a spike in households that have burden. Households with higher incomes started to pay more burdens, which can be attributed to 2007 financial housing market crisis.

@@

From this graph, you can see that the Northeast and West have higher rates of burden at higher income levels, therefore illustrating how housing affordability in these regions are less than that of the Midwest and South.

@@

From this graph, you can take a more indepth look at the relationship between housing costs and burden. It's interesting to see that all three burden lines are close to one another, which illustrates the principle that those with more money aren't buying more expensive houses. From the previous grpah, we saw that those with higher incomes have less burden, and those with lower incomes have higher burden. Each level of burden has similar housing costs, therefore reinforcing the idea that people are buying similar priced housing among the lower and middle classes. Again, a spike around 2010 is prevalent, which can be caused by the 2007 housing crisis.

@@

Conclusion:

Blah blah blah blah blah
